%-------------------------
% Harsh Hirawat - ATS-Optimized Resume v3 (95+ Score)
%-------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue,
  pdfborder={0 0 0}
]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{charter}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands
%-------------------------

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%==========================================================
\begin{document}
%==========================================================

%-----------HEADER-----------
\begin{center}
    {\Huge \scshape \textbf{Harsh Hirawat}} \\ \vspace{4pt}
    \small
    Pune, Maharashtra, India \quad $|$ \quad
    \href{tel:+919479733955}{+91 94797 33955} \quad $|$ \quad
    \href{mailto:harsh@greenhacker.in}{harsh@greenhacker.in} \\ \vspace{2pt}
    \href{https://linkedin.com/in/harshhirawat}{linkedin.com/in/harshhirawat} \quad $|$ \quad
    \href{https://github.com/greenhacker420}{github.com/greenhacker420} \quad $|$ \quad
    \href{https://greenhacker.in}{greenhacker.in}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
Full-stack AI engineer and B.Tech CSE student building production LLM, RAG, and backend systems. Experienced with Python, TypeScript, FastAPI/Express, LangChain, LangGraph, Gemini/OpenAI APIs, Pinecone, PostgreSQL, Redis, Docker, AWS, and Cloudflare. Built and deployed real-world AI products including Campus Connect, AskMyNotes, and real-time voice-agent systems, with measurable impact across latency, uptime, and production traffic.

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:} Python, JavaScript, TypeScript, Go, SQL \\
     \textbf{AI / Machine Learning:} PyTorch, TensorFlow, Scikit-learn, Hugging Face Transformers, MLOps, LLM Fine-Tuning \\
     \textbf{Generative AI \& Agents:} LangChain, LangGraph, LLM APIs (OpenAI, Gemini, Anthropic, Groq, Mistral), RAG (Pinecone, FAISS, pgvector), Agentic Workflows, Prompt Engineering \\
     \textbf{Backend Development:} FastAPI, Node.js, Express, REST APIs, WebSockets, Microservices, Async Architectures, pytest, Unit Testing \\
     \textbf{Frontend Development:} React, Next.js, Tailwind CSS, Server-Side Rendering (SSR) \\
     \textbf{Databases:} PostgreSQL, Redis, MongoDB \\
     \textbf{Cloud / DevOps:} Docker, AWS, GCP, Cloudflare, CI/CD Pipelines, Git, Containerization \\
    }}
\end{itemize}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {Freelance Full-Stack Developer}{Oct 2025 -- Present}
      {MindReader Biotech}{USA (Remote)}
      \resumeItemListStart
        \resumeItem{Architected a subscription-based biotech intelligence platform translating clinical research into actionable investment insights, serving 3+ enterprise clients with secure role-based access and production-grade data workflows.}
        \resumeItem{Built 5+ high-performance analytics dashboards using Next.js and Tailwind CSS, reducing data-to-insight time by $\sim$35\% for end users.}
        \resumeItem{Deployed containerized microservices using Docker, PostgreSQL, and Redis caching, cutting average deployment time by $\sim$50\% via automated CI/CD pipelines.}
        \resumeItem{Implemented AWS and Cloudflare infrastructure with automated failover, achieving $\sim$99.9\% uptime across all production environments.}
      \resumeItemListEnd

    \resumeSubheading
      {AI Engineer Intern}{Oct 2025 -- March 2026}
      {CommKraft}{Remote}
      \resumeItemListStart
        \resumeItem{Architected a low-latency real-time AI voice agent platform using Gemini API, WebRTC streaming, and asynchronous tool orchestration, supporting 200+ concurrent sessions.}
        \resumeItem{Built asynchronous LLM orchestration pipeline with LangChain that reduced agent response latency by $\sim$90\% (from $\sim$3s to under 300ms), improving real-time conversation quality.}
        \resumeItem{Designed a state-driven conversation engine with interruption handling, tool execution, and recovery workflows, achieving sub-500ms recovery from failures.}
        \resumeItem{Implemented human-handoff workflows enabling seamless AI-to-human escalation, reducing escalation handling time by $\sim$60\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Evergreen Classic} $|$ \emph{AI-Powered E-Commerce with WhatsApp Integration}}{}
          \resumeItemListStart
            \resumeItem{Link: \href{https://evergreenclassic.in}{evergreenclassic.in} $|$ \href{https://wa.me/+918446306598?text=Hi}{WhatsApp}}
            \resumeItem{Building a full-stack AI-powered e-commerce platform with WhatsApp Business API integration for conversational commerce, covering order tracking, product discovery, and AI-powered customer support.}
            \resumeItem{Integrating Gemini API-powered recommendation engine and LangChain agentic pipeline to handle customer queries end-to-end, reducing manual support overhead.}
            \resumeItem{Architecting backend with FastAPI, PostgreSQL, and Redis Stack; deployed on AWS Lightsail with Docker containerization and automated CI/CD pipelines and proxied with Cloudflare.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Campus Connect} $|$ \emph{Peer-to-Peer EdTech Mentorship Marketplace}}{}
          \resumeItemListStart
            \resumeItem{Links: \href{https://campus-connect.co.in}{campus-connect.co.in} $|$ \href{https://wa.me/917666280250}{WhatsApp Bot}}
            \resumeItem{Built and deployed a production mentorship marketplace using Next.js, Fastify, PostgreSQL, Redis, Docker, Razorpay, WhatsApp APIs, and Cloudflare.}
            \resumeItem{Served 636k+ requests, 8.5k+ unique visitors, and 27 GB+ data over a 30-day period with production monitoring and caching.}
            \resumeItem{Implemented booking, payments, mentor discovery, college comparison, admin operations, async workers, and notification workflows.}
            \resumeItem{Designed high-availability deployment workflows with PostgreSQL replication, Redis replication, Docker Compose, Cloudflare Tunnel, and automated failover checks.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AskMyNotes} $|$ \emph{Corrective RAG Study Companion}}{}
          \resumeItemListStart
            \resumeItem{Links: \href{https://github.com/GreenHacker420/ASKMYNOTES}{github.com/GreenHacker420/ASKMYNOTES} $|$ \href{https://askmynotes.greenhacker.in}{askmynotes.greenhacker.in}}
            \resumeItem{Built a citation-backed CRAG system for PDFs and text notes using Next.js, Express, TypeScript, PostgreSQL, Pinecone, Gemini, LangGraph, and Socket.IO.}
            \resumeItem{Implemented subject-scoped vector retrieval, semantic re-ranking, threshold gating, and grounded answer generation to reduce hallucinations.}
            \resumeItem{Added real-time streaming chat, voice query support, quiz generation, authentication, and per-user subject isolation.}
            \resumeItem{Processed 1,000+ document chunks and improved retrieval precision by combining semantic similarity with re-ranking.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{ShopControl} $|$ \emph{Mobile-First Shop Operations Platform}}{}
          \resumeItemListStart
            \resumeItem{Link: \href{https://github.com/GreenHacker420/stock-app}{github.com/GreenHacker420/stock-app}}
            \resumeItem{Built a mobile-first operations platform for multi-tenant retail and distribution operations, utilizing a React Native (Expo) frontend and a containerized Node.js (Express) backend.}
            \resumeItem{Implemented a secure PostgreSQL database layout with Prisma ORM, supporting isolated multi-tenant and multi-shop workflows across sales, inventory, and payment collections.}
            \resumeItem{Developed asynchronous task workers using BullMQ and Redis for high-throughput background processing, alongside Socket.IO for real-time monitoring and AWS S3 for secure file assets.}
            \resumeItem{Engineered a custom full-stack Truecaller authentication module (expo-truecaller) for zero-tap mobile verification, with local SQLite caching for offline-first network resilience.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Newton School of Technology (ADYPU)}{Pune, Maharashtra, India}
      {Bachelor of Technology in Computer Science}{Aug 2024 -- May 2028}
      \resumeItemListStart
        \resumeItem{\textbf{CGPA:} 8.86 / 10}
        \resumeItem{\textbf{Relevant Coursework:} Data Structures and Algorithms, Machine Learning, Distributed Systems, Database Management Systems, Operating Systems, Computer Networks, System Design}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Engineer Associate Certificate}{Feb 2026}
      {School of AI -- Udemy}{Online}

    \resumeSubheading
      {AI Hero: 12-Month Journey from Zero to Expert}{Feb 2026}
      {School of AI -- Udemy}{Online}

  \resumeSubHeadingListEnd

%-----------OPEN SOURCE AND ACTIVITIES-----------
\section{Open Source and Activities}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Open Source:} Active GitHub contributor with 500+ commits across AI/ML and full-stack repositories at \href{https://github.com/greenhacker420}{github.com/greenhacker420} \\
     \textbf{Portfolio:} Personal developer platform with project showcase and Gemini AI chatbot at \href{https://greenhacker.in}{greenhacker.in} \\
     \textbf{Key Domains:} LLM systems, RAG pipelines, agentic AI, real-time voice agents, WhatsApp automation, cloud-native deployment, full-stack engineering \\
    }}
\end{itemize}

%==========================================================
\end{document}
